Prefetching SPARQL query cacher

### 2016-07-28 dissertation/cache-proxy.tex
move the description of the clients
reword

The implementation consists of several modules that have been
published to the Comprehensive Perl Archive Network as Free Software,
and most of which have become a part the Free Software ecosystem. For
a detailed account of the modules that are a part of the system and
the authors that have contributed code in this ecosystem, see
Appendix~\ref{app:modules}.

@@

To install the system on the top of a Debian system with only
essential packages requires 146 Debian packages. Running the test
suite requires even more. As such, it builds on the code of hundreds
of authors, too many to enumerate. I shall constrain myself to list
the modules that have code that has been motivated by this
study. Modules that have other primary authors than myself have been
started prior to this present project, but may have substantial
contributions from this project. The Attean framework was started as
part of the effort in Section~\ref{sec:conpush}, but even though it
has been developed further with the requirements that arose from this
project and has contributions from me, the vast majority of the code
has been written by Gregory Todd Williams, who would have been a
co-author of this work had it been published in the peer-reviewed
literature. The main work in this project has gone into the module
\pmodule{AtteanX::Query::Cache}, where I have authored the vast
majority of the code. The relative difference in authorship can be
further examined by checking the linked Github repositories, or by
using git2prov\footnote{See \url{http://git2prov.org/}} to create RDF
data of the commit history. Table~\ref{tab:modules} shows the modules
that have been influenced or written as part of this project.

@@

To further understand the roles of the different modules, note the
following: \pmodule{LWP::UserAgent::CHICaching} is a traits-based
\cite{traits} implementation of the majority of RFC7234.
The underlying caching framework used by this module, \pmodule{CHI},
will take care of expiry and purging of entries, since this module
will supply an explicit freshness lifetime. 
\pmodule{AtteanX::Endpoint} is an implementation of the server side of
SPARQL 1.1 Protocol.

>>>>

The implementation consists of several modules that have been
published to the Comprehensive Perl Archive Network as Free Software,
and most of which have become a part the Free Software ecosystem. For
a detailed account of the modules that are a part of the system and
the authors that have contributed code in this ecosystem, see
Appendix~\ref{app:modules}. Some parts are essential for the
discussion and to understand the contributions, and therefore detailed
in the following:

@@

Installing the system on the top of a Debian system with only
essential packages require 146 Debian packages. Running the test
suite requires even more. As such, it builds on the code of hundreds
of authors, too many to enumerate. I shall constrain myself to list
the modules that have code that has been motivated by this
study. Modules that have other primary authors than myself have been
started prior to this present project, but may have substantial
contributions from this project. The Attean framework was started as
part of the effort in Section~\ref{sec:conpush}, but even though it
has been developed further with the requirements that arose from this
project and has contributions from me, the vast majority of the code
has been written by Gregory Todd Williams, who would have been a
co-author of this work had it been published in the peer-reviewed
literature. The main work in this project has gone into the module
\pmodule{AtteanX::Query::Cache}, where I have authored the vast
majority of the code. The relative difference in authorship can be
further examined by checking the linked Github repositories, or by
using git2prov\footnote{See \url{http://git2prov.org/}} to create RDF
data of the commit history. Table~\ref{tab:modules} shows the modules
that have been influenced or written as part of this project.

@@

To further understand the roles of the different modules, note the
following: \pmodule{LWP::UserAgent::CHICaching} is a traits-based
\cite{traits} implementation of the majority of RFC7234.
The underlying caching framework used by this module, \pmodule{CHI},
will take care of expiry and purging of entries, since this module
will supply an explicit freshness lifetime. 
\pmodule{AtteanX::Endpoint} is an implementation of the server side of
SPARQL 1.1 Protocol. Another two modules require further details:
